\begin{acknowledgements}

\noindent I'm in so much debt to many people who have been part of this enjoyable journey, but first and foremost I would like to thank my supervisors Prof. Min Chen, Prof. Jim Davies and Dr. Susanna-Assunta Sansone. 


To Min Chen who took me as a raw DPhil student and through his support, patience, guidance, and endless energy has helped guide me through the entire process. 
It has been a great pleasure to work with someone held in such high esteem by the visualization community and I am so fortunate to have been given the chance to conduct my DPhil with him.


To Susanna-Assunta Sansone who has given me the freedom to pursue a DPhil whilst conducting research and the Oxford e-Research Centre (OeRC) for supporting this process. 
We have worked together for six years now, and I have enjoyed being in her growing group and seeing things go from strength to strength.

To Philippe Rocca-Serra who has also put up with me for six years now, interspersed with my delightfully accurate French accent. 
Philippe is a great friend who has been a tremendous support through all stages of this journey, in particular the more difficult ones. 

To Annapaola Santarsiero who has dealt with the many late nights and weekend work for three years whilst always being supportive.
Annapaola even agreed to marry me when I proposed during the writing up process!

Additionally, I owe a great deal to my incredibly talented friends and colleagues at the OeRC who have made my time in Oxford so great.
Their knowledge, passion, friendliness, and availability to share their knowledge has been amazing.
In particular I wish to thank Alejandra González-Beltrán, Simon Walton, Alfie Abdul-Rahman, Brian Duffy, Endre Lászió, Piotr Łopatka, Ramon Granell, Raz Lakhoo, Stef Salvini, Istvan Reguly, Ségolène Tarte (who also endured my French accents), Milo Thurston, Neil Caithness, Bas van Schaik, Kay Sutton, Ross McCartney, Clem Harris, and David DeRoure. 

Finally to my great network of friends in Oxford and beyond who have all in some way played a part in my journey, including Tommy Barr, Ryan McCrea, David Close, Liam Kelly, Matt Brinklow, Devan Govender, James Malone, Will McClaren, Rasmus Wissman, Sam Whitehead, Chris Boddy, Dan Short, Ian Robertson, Caterina Doglioni, and so many more!

I would also like to thank and remember the contributions of Professor Matthew Ward who researched glyphs extensively and contributed a large amount of knowledge in the direction of glyph-based visualization.
Professor Ward was to present with Dr. Rita Borgo, Prof. Min Chen, and Prof. Sine McDougall at the glyph tutorial at VIS 2014 in Paris, but sadly passed away in October 2014.

\end{acknowledgements}
