\begin{publications}

\noindent\textbf{Publications}

\noindent The work conducted in this thesis has led to the following publications. \\

\noindent \textbf{E. Maguire}‚ P. Rocca-Serra‚ S.-A. Sansone‚ J. Davies, and M. Chen. \emph{Taxonomy-based Glyph Design - with a Case Study on Visualizing Workflows of Biological Experiments}. In IEEE Transactions on Visualization and Computer Graphics, Pages 2603-2612, Volume 18 (2012).\\

\noindent R. Borgo, J. Kehrer, D.H.S. Chung, \textbf{E. Maguire}, R. S. Laramee, H. Hauser, M. Ward, and M. Chen. \emph{Glyph-based visualization: Foundations, design guidelines, techniques and applications}. In Eurographics State of the Art Reports, EG STARs (2013), Pages 39-63.\\

\noindent A. Abdul-Rahman, J. Lein, K. Coles, \textbf{E. Maguire}, M. Meyer, M. Wynne, C. R. Johnson, A. Trefethen, and M. Chen. \emph{Rule-based Visual Mappings - with a Case Study on Poetry Visualization}. In Computer Graphics Forum, Pages 381-390, Volume 32 (2013).\\

\noindent \textbf{E. Maguire}‚ P. Rocca-Serra‚ S.-A. Sansone‚ J. Davies, and M. Chen. \emph{Visual Compression of Workflow Visualizations with Automated Detection of Macro Motifs}. In IEEE Transactions on Visualization and Computer Graphics, Pages 2576-2585, Volume 19 (2013).\\

\noindent A. Abdul-Rahman‚ \textbf{E. Maguire} and M. Chen. \emph{Comparing Three Designs of Macro-Glyphs for Poetry Visualization}. In Proceedings of EuroVis 2014‚ Short Paper (2014).\\

\noindent \textbf{E. Maguire}‚ P. Rocca-Serra‚ S.-A. Sansone, and M. Chen. \emph{Redesigning the Sequence Logo with Glyph-based Approaches to Aid Interpretation}. In Proceedings of EuroVis 2014‚ Short Paper (2014).\\

\noindent S. Walton, \textbf{E. Maguire}‚ and M. Chen. \emph{Multiple Queries with Conditional Attributes (QCATs) for Anomaly Detection and Visualization}. In Proceedings of the Eleventh Workshop on Visualization for Cyber Security, VizSec 2014.\\

\noindent\textbf{Tutorials}\\

\noindent \emph{Glyph-based visualization tutorial} - presented at IEEE VIS 2014. Co-organized with R. Borgo and M. Chen. 

\end{publications}
