\chapter{Preliminaries}
\label{chap:related_work}
This chapter aims to introduce the overarching concepts of glyph-based visualizations. 
The first section provides a grounding on the building blocks of visualizations. 
These blocks are often named as the \emph{visual channels}, of which there are many. 
These are processed by the visual system which we detail in full.
Our visual system and knowledge of how these visual channels are processed forms the basis of concepts such as \emph{pre-attentive processing}, \emph{channel composition}, \emph{global/local features}, \emph{top-down vs bottom-up processing} and so on which are often mentioned in the literature. 
These concepts are important when constructing any visualization since an understanding of how humans process visual information should allow for better visualization design.

The second section introduces glyphs and glyph-based visualization.
We introduce the history of glyphs, their application areas, and finally, their limitations.

\input{chapters/relatedwork-visual}

\input{chapters/relatedwork-glyphs}

\section{Summary}

Glyphs have so far made a large contribution to the visualization literature and have already been employed in a large number of domains as exemplified in Section \ref{sec:glyph-examples}. 

However, there are some criticisms of glyphs made by Lee \etal \cite{Lee03anempirical} and Morris \etal \cite{morris2000experimental}. 
Lee \etal found that users asked to perform data comparison tasks (largest value/smallest value tasks) were slower, less accurate and users were less confident when using glyphs compared to spatial representations (scatter plots in this case). 
As detailed in earlier parts of this chapter, position is a very powerful visualization primitive for the display of data. 
Spatial representations featuring only two dimensions are inevitably going to provide more favourable results than glyphs with no spatial arrangement.

True advantages may be obtained through using glyphs when there is a need to represent many dimensions, not just two quantitative dimensions where spatial representations will perform very well. 
Techniques such as parallel coordinates will allow for visualization of many dimensions at once, however the spatial information is lost.
Glyphs, as stated earlier have the power to represent many more dimensions with the additional advantage of using spatial information to position glyphs in 2D or 3D space.  

The key problem in creating glyphs also identified by Ward \cite{ward02} and Lee \etal \cite{Lee03anempirical} is in deciding which visual channels outlined in Section \ref{sec:retinal_variables} should represent data attributes. 
For example, using colour to indicate categories that have no associated colour in the real world is not a suitable mapping.
Similarly, using shape to represent categories with no obvious shape association is also not a good mapping.
This is the most probable reason for the poor performance of Chernoff faces in an evaluation by Morris \etal \cite{morris2000experimental}.

There are many examples of such visual mappings in the examples listed in Section \ref{sec:glyph-examples} which use too many abstract mappings in their glyph design. 

Ideally we wish to make glyphs easier to decipher, display information more accurately, and present important information in the most visually accessible way. 
This can be achieved through following the perceptual knowledge outlined in Sections \ref{sec:retinal_variables}, \ref{sec:channel-composition}, \ref{sec:global_local_processing}, \ref{sec:topdown_bottomup}, and \ref{sec:popout}. 
Section \ref{sec:retinal_variables} for instance details the visual channels that are best for representing quantitative and qualitative information. 

The goal of this thesis is to address the limitations of glyphs through systemising their design.
This will involve incorporating the psychological and neurophysiological information presented in this chapter into a more formal process for glyph design. 
The exact mechanism we propose for accomplishing this is discussed next chapter which will outline some of the possible strategies we may employ to enable this systemisation. 
